---
title: "Integration tests"
output: github_document
---

```{r knitr_setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

![packageversion](https://img.shields.io/badge/Package%20version-`r unname(desc::desc_get("Version"))`-orange.svg?style=flat-square)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-','--', Sys.Date())`-yellowgreen.svg)](/commits/master)

```{r setup, include=FALSE, message=FALSE}
library(rmo)
set.seed(1623L)
n <- 1e3L

ks_test <- function(n, d, FUN, intensities, normalize=FALSE) {
  scale <- sum(intensities)
  if (normalize) {
    intensities <- intensities / scale
    scale <- 1
  }
  ks.test(scale * apply(FUN(n, d, intensities), 1, min), pexp)
}

ex_ks_test <- function(n, d, FUN, ex_intensities, normalize=FALSE) {
  scale <- sum(ex_intensities)
  if (normalize) {
    ex_intensities <- ex_intensities / scale
    scale <- 1
  }
  ks.test(
    scale * apply(FUN(n, d, ex_intensities), 1, min), pexp
  )
}

cuadras_auge_ks_test <- function(n, d, FUN, alpha, beta, normalize=FALSE) {
  scale <- (alpha * d + beta)
  if (normalize) {
    alpha <- alpha / scale
    beta <- beta / scale
    scale <- 1
  }
  ks.test(
    scale *
      apply(FUN(n, d, alpha, beta), 1, min), pexp
  )
}

lfm_ks_test <- function(
                        n, d, FUN, rate, rate_killing, rate_drift, rjump_name, rjump_arg_list, normalize=FALSE) {
  if ("rposval" == rjump_name) {
    scale <- rate_killing + rate_drift * d + rate * (1 - exp(-rjump_arg_list$value * d))
  } else if ("rexp" == rjump_name) {
    scale <- rate_killing + rate_drift * d + rate * d / (d + rjump_arg_list$rate)
  } else if ("rpareto" == rjump_name) {
    scale <- rate_killing + rate_drift * d + rate *
      integrate(function(x, alpha, x0) (1 - exp(-x * d)) * alpha * x0^alpha / x^(alpha + 1), 0, Inf, alpha = rjump_arg_list$alpha, x0 = rjump_arg_list$x0)$value
  }
  if (normalize) {
    rate <- rate / scale
    rate_drift <- rate_drift / scale
    rate_killing <- rate_killing / scale
    scale <- 1
  }
  ks.test(apply(FUN(
    n, d, rate, rate_killing, rate_drift,
    rjump_name, rjump_arg_list
  ), 1, min) * scale, pexp)
}
```

## The overall minimum

For a Marshall--Olkin distributed random vector \( \boldsymbol{\tau} \) with parameters \( \lambda_{I} \), \( \emptyset \neq I \subseteq {\{ 1 , \ldots , d \}} \), we have that
\[
  \min_{i \in {\{ 1 , \ldots , d \}}} \tau_i
\]
is exponentially distributed with rate \( \lambda = \sum_{\emptyset \neq I \subseteq {\{ 1 , \ldots , d \}}} \lambda_{I} \).

In the following, we test this with a Kolmogorov-Smirnov test (`ks.test`).


### Test for `rmo_esm`

```{r overall-minimum-esm}
d <- 10L

ks_test(n, d, rmo_esm, intensities_constant(d, constant = 0.3))
ks_test(n, d, rmo_esm, intensities_linear(d, scale = 0.2))
ks_test(n, d, rmo_esm, intensities_armageddon(d, alpha = 0.6, beta = 0.2))
ks_test(n, d, rmo_esm, intensities_poisson(d, eta = 0.4))
ks_test(n, d, rmo_esm, intensities_alpha_stable(d, alpha = 0.4))
ks_test(n, d, rmo_esm, intensities_exponential(d, lambda = 0.5))
ks_test(n, d, rmo_esm, intensities_gamma(d, a = 0.6))
ks_test(n, d, rmo_esm, intensities_pareto(d, alpha = 0.4, x0 = 1e-4))
ks_test(n, d, rmo_esm, intensities_inverse_gaussian(d, eta = 0.1))

ks_test(n, d, rmo_esm, intensities_constant(d, constant = 0.3), normalize = TRUE)
ks_test(n, d, rmo_esm, intensities_linear(d, scale = 0.2), normalize = TRUE)
ks_test(n, d, rmo_esm, intensities_armageddon(d, alpha = 0.6, beta = 0.2), normalize = TRUE)
ks_test(n, d, rmo_esm, intensities_poisson(d, eta = 0.4), normalize = TRUE)
ks_test(n, d, rmo_esm, intensities_alpha_stable(d, alpha = 0.4), normalize = TRUE)
ks_test(n, d, rmo_esm, intensities_exponential(d, lambda = 0.5), normalize = TRUE)
ks_test(n, d, rmo_esm, intensities_gamma(d, a = 0.6), normalize = TRUE)
ks_test(n, d, rmo_esm, intensities_pareto(d, alpha = 0.4, x0 = 1e-4), normalize = TRUE)
ks_test(n, d, rmo_esm, intensities_inverse_gaussian(d, eta = 0.1), normalize = TRUE)
```

### Test for `rmo_arnold`

```{r overall-minimum-arnold}
d <- 10L

ks_test(n, d, rmo_arnold, intensities_constant(d, constant = 0.3))
ks_test(n, d, rmo_arnold, intensities_linear(d, scale = 0.2))
ks_test(n, d, rmo_arnold, intensities_armageddon(d, alpha = 0.6, beta = 0.2))
ks_test(n, d, rmo_arnold, intensities_poisson(d, eta = 0.4))
ks_test(n, d, rmo_arnold, intensities_alpha_stable(d, alpha = 0.4))
ks_test(n, d, rmo_arnold, intensities_exponential(d, lambda = 0.5))
ks_test(n, d, rmo_arnold, intensities_gamma(d, a = 0.6))
ks_test(n, d, rmo_arnold, intensities_pareto(d, alpha = 0.4, x0 = 1e-4))
ks_test(n, d, rmo_arnold, intensities_inverse_gaussian(d, eta = 0.1))

ks_test(n, d, rmo_arnold, intensities_constant(d, constant = 0.3), normalize = TRUE)
ks_test(n, d, rmo_arnold, intensities_linear(d, scale = 0.2), normalize = TRUE)
ks_test(n, d, rmo_arnold, intensities_armageddon(d, alpha = 0.6, beta = 0.2), normalize = TRUE)
ks_test(n, d, rmo_arnold, intensities_poisson(d, eta = 0.4), normalize = TRUE)
ks_test(n, d, rmo_arnold, intensities_alpha_stable(d, alpha = 0.4), normalize = TRUE)
ks_test(n, d, rmo_arnold, intensities_exponential(d, lambda = 0.5), normalize = TRUE)
ks_test(n, d, rmo_arnold, intensities_gamma(d, a = 0.6), normalize = TRUE)
ks_test(n, d, rmo_arnold, intensities_pareto(d, alpha = 0.4, x0 = 1e-4), normalize = TRUE)
ks_test(n, d, rmo_arnold, intensities_inverse_gaussian(d, eta = 0.1), normalize = TRUE)
```


### Test for `rexmo_markovian` with `d = 10`

```{r overall-minimum-ex_arnold-10}
d <- 10L

ex_ks_test(n, d, rexmo_markovian, ex_intensities_constant(d, constant = 0.3))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_linear(d, scale = 0.2))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_armageddon(d, alpha = 0.6, beta = 0.2))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_poisson(d, lambda = 0.3, eta = 0.4))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_alpha_stable(d, alpha = 0.4))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_exponential(d, lambda = 0.5))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_gamma(d, a = 0.6))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_pareto(d, alpha = 0.4, x0 = 1e-4))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_inverse_gaussian(d, eta = 0.1))

ex_ks_test(n, d, rexmo_markovian, ex_intensities_constant(d, constant = 0.3), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_linear(d, scale = 0.2), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_armageddon(d, alpha = 0.6, beta = 0.2), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_poisson(d, lambda = 0.3, eta = 0.4), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_alpha_stable(d, alpha = 0.4), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_exponential(d, lambda = 0.5), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_gamma(d, a = 0.6), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_pareto(d, alpha = 0.4, x0 = 1e-4), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_inverse_gaussian(d, eta = 0.1), normalize = TRUE)
```


### Test for `rexmo_markovian` with `d = 125`

```{r overall-minimum-ex_arnold-125}
d <- 125L

ex_ks_test(n, d, rexmo_markovian, ex_intensities_constant(d, constant = 0.3))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_linear(d, scale = 0.2))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_cuadras_auge(d, alpha = 0.6, beta = 0.2))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_poisson(d, lambda = 0.3, eta = 0.4))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_alpha_stable(d, alpha = 0.4))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_exponential(d, lambda = 0.5))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_gamma(d, a = 0.6))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_pareto(d, alpha = 0.4, x0 = 1e-4))
ex_ks_test(n, d, rexmo_markovian, ex_intensities_inverse_gaussian(d, eta = 0.1))

ex_ks_test(n, d, rexmo_markovian, ex_intensities_constant(d, constant = 0.3), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_linear(d, scale = 0.2), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_cuadras_auge(d, alpha = 0.6, beta = 0.2), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_poisson(d, lambda = 0.3, eta = 0.4), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_alpha_stable(d, alpha = 0.4), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_exponential(d, lambda = 0.5), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_gamma(d, a = 0.6), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_pareto(d, alpha = 0.4, x0 = 1e-4), normalize = TRUE)
ex_ks_test(n, d, rexmo_markovian, ex_intensities_inverse_gaussian(d, eta = 0.1), normalize = TRUE)
```


### Test `rmo_esm_cuadras_auge` with `d = 10`

```{r overall-minimum-cuadras-auge-10}
d <- 10L

cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0.3, 0)
cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0, 0.3)
cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0.6, 0.3)

cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0.3, 0, normalize = TRUE)
cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0, 0.3, normalize = TRUE)
cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0.6, 0.3, normalize = TRUE)
```


### Test `rmo_esm_cuadras_auge` with `d = 125`

```{r overall-minimum-cuadras-auge-125}
d <- 125L

cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0.3, 0)
cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0, 0.3)
cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0.6, 0.3)

cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0.3, 0, normalize = TRUE)
cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0, 0.3, normalize = TRUE)
cuadras_auge_ks_test(n, d, rmo_esm_cuadras_auge, 0.6, 0.3, normalize = TRUE)
```


### Test `rmo_lfm_cpp` with `d = 10`

```{r overall-minimum-lfm_cpp-10}
d <- 10L

lfm_ks_test(n, d, rmo_lfm_cpp, 0, 0.3, 0, "rposval", list("value" = 1))
lfm_ks_test(n, d, rmo_lfm_cpp, 0, 0, 0.4, "rposval", list("value" = 1))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rposval", list("value" = 2))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rposval", list("value" = 2))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rexp", list("rate" = 0.6))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rexp", list("rate" = 0.6))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rpareto", list("alpha" = 0.4, "x0" = 1e-4))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rpareto", list("alpha" = 0.4, "x0" = 1e-4))

lfm_ks_test(n, d, rmo_lfm_cpp, 0, 0.3, 0, "rposval", list("value" = 1), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0, 0, 0.4, "rposval", list("value" = 1), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rposval", list("value" = 2), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rposval", list("value" = 2), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rexp", list("rate" = 0.6), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rexp", list("rate" = 0.6), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rpareto", list("alpha" = 0.4, "x0" = 1e-4), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rpareto", list("alpha" = 0.4, "x0" = 1e-4), normalize = TRUE)
```


### Test `rmo_lfm_cpp` with `d = 125`

```{r overall-minimum-lfm_cpp-125}
d <- 125L

lfm_ks_test(n, d, rmo_lfm_cpp, 0, 0.3, 0, "rposval", list("value" = 1))
lfm_ks_test(n, d, rmo_lfm_cpp, 0, 0, 0.4, "rposval", list("value" = 1))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rposval", list("value" = 2))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rposval", list("value" = 2))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rexp", list("rate" = 0.6))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rexp", list("rate" = 0.6))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rpareto", list("alpha" = 0.4, "x0" = 1e-4))
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rpareto", list("alpha" = 0.4, "x0" = 1e-4))

lfm_ks_test(n, d, rmo_lfm_cpp, 0, 0.3, 0, "rposval", list("value" = 1), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0, 0, 0.4, "rposval", list("value" = 1), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rposval", list("value" = 2), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rposval", list("value" = 2), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rexp", list("rate" = 0.6), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rexp", list("rate" = 0.6), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0, 0, "rpareto", list("alpha" = 0.4, "x0" = 1e-4), normalize = TRUE)
lfm_ks_test(n, d, rmo_lfm_cpp, 0.1, 0.2, 0.4, "rpareto", list("alpha" = 0.4, "x0" = 1e-4), normalize = TRUE)
```
