---
title: "An introduction to `rmo`"
output: github_document
---

```{r knitr_setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Summary

In this notebook, we will benchmark the runtime of the various sampling algorithms which are implemented in this package.

## Setup

Appart from this package, we require the following packages:

- `bench` (for benchmarks),
- `magrittr`, `dplyr`, `tidyr` (data manipulation), and
- `ggplot2`, `ggbeeswarm`, `scales` (plotting).

```{r setup, message=FALSE}
library("rmo")

library("bench")

library("magrittr")
library("purrr")
library("dplyr")
library("tidyr")

library("ggplot2")
library("ggbeeswarm")
library("scales")
```

## Cuadras-Augé parametrisation

The Cuadras-Augé parametrisation corresponds to an exchangeable exogenous shock
model with individual shocks with rate \( \alpha \) and a global shock with rate
\( \beta \).

The Bernstein function is
\[
  \psi(x)
    = \beta  + x \alpha ,
    \quad x > 0 .
\]

### Create a Bernstein function instance

We can create an instance of the corresponding Bernstein function using the
package

```{r Cuadras-Auge-bf}
alpha <- 0.6
beta <- 0.2
bf_const <- ConstantBernsteinFunction(constant=beta)
bf_lin <- LinearBernsteinFunction(scale=alpha)
bf <- SumOfBernsteinFunctions(first=bf_const, second=bf_lin)
bf
```

### Calculate the ex-intensity parameters

The rate parameters for the exchangeable Marshall--Olkin model can be calculated
with the following formula
\[
  \lambda_i
    = {(-1)}^{i-1} \Delta^{i} \psi{(d-i)},
    \quad i \in {\{ 1 , \ldots , d \}} .
\]

This can be done manually as follows

```{r Cuadras-Auge-ex_intensities-1}
d <- 5
psi_values <- map_dbl(0:d, ~{
  valueOf(bf, .x, 0L)
})
ex_intensities <- map_dbl(1:d, ~{
  (-1)^(.x-1) * diff(psi_values[1+(d-.x):d], differences=.x)
})
```

> __Disclaimer__: The approach above is not recommended to be used in practice
> and only included to demonstrate how to use the Bernstein function classes.


Manually calculating iterated differences is numerically unstable and ultimately
can lead to negative intensities. For this reason, these differences are
internally calculated with a different representation. This can be used as
follows

```{r Cuadras-Auge-ex_intensities-2}
d <- 5
ex_intensities <- map_dbl(1:d, ~{
  ## (-1)^{.x-1} \Delta^{.x} \psi(d-.x)
  valueOf(bf, d-.x, difference_order=.x)
})
```


### Drop-in wrappers to create ex-intensity parameters

For some specific Bernstein functions, we provide convenience wrappers to do
this in a more concise way. Here we could do

```{r Cuadras-Auge-ex_intensities-3}
d <- 5
ex_intensities <- ex_intensities_cuadras_auge(d, alpha, beta)
qplot(1:d, ex_intensities)
```

There is more:

- Poisson subordinator BF
- Gamma subordinator BF
- Alpha Stable subordinator BF


### Create intensities parameter

```{r Cuadras-Auge-exlambda-general}
d <- 5
intensities <- intensities_cuadras_auge(d, alpha, beta)
qplot(1:(2^d-1), intensities)
```


### Benchmark

- We have the Cuadras-Augé parametrisation \( \alpha, \beta \geq 0 \) with
    \( \alpha + \beta > 0 \).
- We can calculate the representations \( \lambda_i, i \in {\{ 1, \ldots, d \}} \)
   and \( \lambda_I, \emptyset \neq I \subseteq {\{ 1 , \ldots , d \}} \)
   as above from \( \psi \).
- This parametrisation corresponds to a LFM with drift \( \alpha \) and
    killing rate \( \beta \).

```{r Cuadras-Auge-benchmark-1, message=FALSE, fig.width=8, fig.height=8}
n <- 1e4
d <- c(3L, 10L)
alpha <- c(0.1, 0.4, 0.8)
beta <- c(0.1, 0.4, 0.8)

bp1 <- bench::press(
  "d" = d,
  "alpha" = alpha,
  "beta" = beta,
  {
    ex_intensities <- ex_intensities_cuadras_auge(d, alpha, beta)
    intensities <- intensities_cuadras_auge(d, alpha, beta)
    force(ex_intensities)
    force(intensities)
    bench::mark(
      Cuadras_Auge = rmo:::Rcpp__rmo_esm_cuadras_auge(n, d, alpha, beta),
      Ex_Arnold = rmo:::Rcpp__rmo_ex_arnold(n, d, ex_intensities),
      LFM = rmo:::Rcpp__rmo_lfm_cpp(
        n, d, 0, beta, alpha, "rposval", list("value" = 1)),
      Arnold = rmo:::Rcpp__rmo_arnold(n, d, intensities),
      ESM = rmo:::Rcpp__rmo_esm( n, d, intensities),
      min_iterations = 100L,
      check=FALSE
    )
  }
)

bp1 %>%
  unnest(cols = c("time", "gc")) %>%
  mutate(expression = factor(
    expression,
    levels = c("Cuadras_Auge", "Ex_Arnold", "LFM", "Arnold", "ESM")
    )) %>%
  ggplot(aes(expression, time, colour = gc)) +
  ggbeeswarm::geom_quasirandom() +
  ggplot2::coord_flip() +
  theme(legend.position = "bottom") +
  facet_grid(d + alpha ~ beta)
```


```{r Cuadras-Auge-benchmark-2, message=FALSE, fig.width=8, fig.height=8}
n <- 1e4
d <- c(3L, 10L, 15L)
alpha <- 0.8
beta <- 0.4

bp2 <- bench::press(
  "d" = d,
  {
    ex_intensities <- ex_intensities_cuadras_auge(d, alpha, beta)
    intensities <- intensities_cuadras_auge(d, alpha, beta)
    force(ex_intensities)
    force(intensities)
    bench::mark(
      Cuadras_Auge = rmo:::Rcpp__rmo_esm_cuadras_auge(n, d, alpha, beta),
      Ex_Arnold = rmo:::Rcpp__rmo_ex_arnold(n, d, ex_intensities),
      LFM = rmo:::Rcpp__rmo_lfm_cpp(
        n, d, 0, beta, alpha, "rposval", list("value" = 1)),
      Arnold = rmo:::Rcpp__rmo_arnold(n, d, intensities),
      ESM = rmo:::Rcpp__rmo_esm(n, d, intensities),
      min_iterations = 100L,
      check=FALSE
    )
  }
)

bp2 %>%
  unnest(cols = c("time", "gc")) %>%
  mutate(expression = factor(
    expression,
    levels = c("Cuadras_Auge", "Ex_Arnold", "LFM", "Arnold", "ESM")
    )) %>%
  filter(gc == "none") %>%
  ggplot(aes(x=d, y=time)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, colour = "grey50", formula = y ~ x + I(x^2)) +
  theme(legend.position = "bottom") +
  facet_grid(expression ~ .)
```
