---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(rmo)
```

# rmo

<!-- badges: start -->
![minimal R version](https://img.shields.io/badge/R%3E%3D-3.6.1-6666ff.svg)
![packageversion](https://img.shields.io/badge/Package%20version-0.0.0.9000-orange.svg?style=flat-square)
[![Travis build status](https://travis-ci.org/hsloot/rmo.svg?branch=master)](https://travis-ci.org/hsloot/rmo)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/hsloot/rmo?branch=master&svg=true)](https://ci.appveyor.com/project/hsloot/rmo)
[![Codecov test coverage](https://codecov.io/gh/hsloot/rmo/branch/master/graph/badge.svg)](https://codecov.io/gh/hsloot/rmo?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
<!-- badges: end -->

An R package for the *Marshall-Olkin distribution*: algorithms for the construction, simulation and estimation.

## Motivation

While the academic literature on the Marshall-Olkin distributions is extensive, an intuitive and easy to use implementation is still missing. This project aims to provide an `R` package makes it simple and fun to use Marshall-Olkin distributions for research and real-world applications.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hsloot/rmo")
```

## Example

```{r, include=TRUE}
# library(rmo)
rmo_esm(n = 10, d = 2, intensities = c(1, 1, 1))
```

## License

MIT [Henrik Sloot]()
