---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(rmo)
set.seed(1623)
```

# rmo

<!-- badges: start -->
![minimal R version](https://img.shields.io/badge/R%3E%3D-3.6.1-6666ff.svg)
![packageversion](https://img.shields.io/badge/Package%20version-`r unname(desc::desc_get("Version"))`-orange.svg?style=flat-square)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Travis build status](https://travis-ci.org/hsloot/rmo.svg?branch=master)](https://travis-ci.org/hsloot/rmo)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/hsloot/rmo?branch=master&svg=true)](https://ci.appveyor.com/project/hsloot/rmo)
[![Codecov test coverage](https://codecov.io/gh/hsloot/rmo/branch/master/graph/badge.svg)](https://codecov.io/gh/hsloot/rmo?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-','--', Sys.Date())`-yellowgreen.svg)](/commits/master)
<!-- badges: end -->

An R package for the *Marshall-Olkin distribution*: algorithms for the construction, simulation and estimation.

## Motivation

While the academic literature on the Marshall-Olkin distributions is extensive,
an intuitive and easy to use implementation is still missing. This project aims
to provide an `R` package makes it simple and fun to use Marshall-Olkin
distributions for research and real-world applications.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r, include=TRUE, eval=FALSE}
# install.packages("devtools")
devtools::install_github("hsloot/rmo")
```

## Example

```{r, include=TRUE}
# library(rmo)
rmo_esm(n=10L, d=2L, intensities=c(1, 1, 1))
```


## Roadmap for future development

We are planning to develop the package incrementally. The packages API might
change frequently without deprecation. The goal is to implement prototypes of
the algorithms in `R` and refactor them in compiled code afterwards. The
original `R` implementations are supposed to serve as test functions in the
unit-test harness. Our next steps are:

- __Version 0.2__: Re-implementation of these sampling routines in `C++` with
  `Rcpp` to improve performance.

Other ideas for the future:

- Implementation of estimation routines (__help wanted__).
- An *OOP* implementation of the Marshall--Olkin distribution with the ultimate
  goal to facilitate a hierarchical construction of Marshall--Olkin
  distributions.

## Contributing

Contribution is highly appreciated. Contribution can range from improving the
documentation, writing tests, or raising issues and feature requests to
implementing feature requests or fixing bugs. If you consider to contribute,
have a look at our [contribution guide](.github/CONTRIBUTING.md).



## License

MIT Henrik Sloot
