---
output: github_document
references:
  - id: Sloot2022a
    type: article-journal
    title: Implementing Markovian models for extendible Marshall–Olkin distributions
    author: 
      family: Sloot
      given: Henrik
    container-title: Dependence Modeling
    publisher: De Gruyter
    volume: 10
    issue: 1
    page: 308-343
    DOI: 10.1515/demo-2022-0151
    issued:
      year: 2022
      month: 12
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(rmo)
library(tidyverse)
library(ggplot2)
set.seed(1623)
```

# rmo

<!-- badges: start -->
![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.0-6666ff.svg)
![packageversion](https://img.shields.io/badge/Package%20version-`r unname(desc::desc_get("Version"))`-orange.svg?style=flat-square)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-','--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![R build status](https://github.com/hsloot/rmo/workflows/check-full/badge.svg)](https://github.com/hsloot/rmo/actions)
[![Codecov test coverage](https://codecov.io/gh/hsloot/rmo/branch/master/graph/badge.svg)](https://codecov.io/gh/hsloot/rmo?branch=main)
<!-- badges: end -->

An R package for constructing and simulating high-dimensional
*Marshall-Olkin (MO) distributions*, making it simple and fun to use them for
research and real-world applications. Read more about simulating
high-dimensional MO distributions in [@Sloot2022a].

## Installation

You can install the development version from GitHub using the `devtools` package
with:

```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("hsloot/rmo")
```

## Basic usage

Simulating high-dimensional Marshall–Olkin distributions is made simple with the
`rpextmo()` function. Here is a basic example: 

```{r basic-usage}
rpextmo(
  n = 10,                # number of samples
  d = 3,                 # dimension
  eta = log2(2 - 0.5),   # distribution family parameter
  family = "AlphaStable" # distribution family
)
```

## Advanced usage

All parametric families are linked to *so-called* Bernstein functions. The class
of Bernstein functions is closed under addition, scaling, and composite scaling.
You can create new Bernstein functions and simulate from them. Here is an
example:

```{r advanced-usage}
# Create a custom Bernstein function parametrization
alpha <- log2(2 - 0.5)
x0 <- 5e-4
bf <- SumOfBernsteinFunctions(
  first = LinearBernsteinFunction(
    scale = alpha * x0^(1 - alpha) / (1 - alpha) / gamma(1 - alpha)
  ),
  second = ScaledBernsteinFunction(
    scale = x0^(-alpha) / gamma(1 - alpha),
    original = ParetoBernsteinFunction(
      alpha = alpha,
      x0 = x0
    )
  )
)

# Simulate from the custom Bernstein function parametrization
rextmo(n = 10, d = 3, bf = bf)
```

## Word(s) of caution

While the package is extensively tested, numerical issues may arise in
high-dimensional simulations due to very small or large numbers. We recommend
performing statistical tests suitable for your use-case to ensure validity. For
more guidance, refer to our [statistical unit
tests](https://github.com/hsloot/rmo/blob/main/tests/testthat/test-statistical-unit-test.R)
and submit an [issue
report](https://github.com/hsloot/rmo/issues/new?assignees=&labels=bug&template=statistical_problem.md&title=%5BSTAT%5D)
if you encounter statistical problems.

Additionally, note that while the package reached a certain level of stability,
it is still under active development. We aim to keep the interface of the
primary function `rpextmo()` backwards compatible, the implementation may
undergo changes.

## API documentation

The package is documented using `roxygen2` and `pkgdown`. You can find the
documentation on the [project website](reference/index.html).

## Testing

The package is tested using `testthat`. You can run the tests using the
following command after checking out the repository: 

```{r testing, eval=FALSE}
devtools::test()
```

## Changelog

The changelog is available in the [NEWS.md](NEWS.md) file.

## Contributing

Contributions to `rmo` are welcome! You contribution can be about improving the
documentation, writing tests, raising issues or feature requests, implementing
feature requests, or fixing bugs. Check out our [contribution
guide](.github/CONTRIBUTING.md) to get started.

## References

<div id="refs"></div>

## License

GPL-3 Henrik Sloot
