---
title: "Using `rmo`"
bibliography: ../inst/REFERENCES.bib
output: 
  rmarkdown::html_vignette:
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Using `rmo`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  class.source = "fold-none"
)

library(rmo)

set.seed(1623)
```

The following demonstrates how to use the `rmo` package to generate samples from
a multivariate Marshall–Olkin distribution.

## Simple usage

Sampling from one of the integrated family of *extendible Marshall–Olkin
distributions* is simple. For example, the following code generates a sample of 
size 10 from a trivariate extendible Marshall–Olkin distribution from the 
so-called \( \alpha \)-stable family with parameter \( \alpha = 0.4 \):

```{r}
rpextmo(10, 3, eta = 0.4, family = "AlphaStable")
```

The jump distribution parameter `eta` usually allows for a range of possible 
depenence structures.

## Extended usage

Each integrated family of extendible Marshall–Olkin distributions has the
additional parameters

- `a` (default: 0) for the *killing rate*,
- `b` (default: 0) for the * drift*, and
- `gamma` (default: 1) for the *intensity scaling parameter*.

We cite [@Sloot2022a] for a better understanding of these parameters:

> For this, recall that we can characterize every ext. MO distribution by a
> Bernstein function \( \psi \), which defines the law of a (potentially killed)
> Lévy subordinator. Components corresponding to the ext. MO distributed random
> vector are killed once the subordinator passes their individual unit
> exponential barrier values. For compound Poisson subordinators, we distinguish
> subordinator laws by their jump intensity and jump size distribution: The jump
> intensity translates into the overall speed with which the subordinator
> surpasses the barrier values. Thus, it corresponds to the random vector's
> marginal rate. The distribution of jump sizes predefines the chances of the
> subordinator simultaneously surpassing multiple barrier values, and therefore,
> it corresponds to the random vector's dependence structure. Simply put, a high
> probability of larger jumps increases the chance of simultaneous deaths, while
> a high probability of smaller jumps increases the likelihood of individual
> deaths. This logic culminates into the pure-drift and pure-killing corner
> cases, corresponding to the independence and comonotonicity, respectively,
> pure-jump Lévy subordinators with infinite activity, which can be approximated
> by compound Poisson processes, and convex combinations of those above.

The following code generates a sample of size 10 from a trivariate extendible
Marshall–Olkin distribution from the (extended) *\( \alpha \)-stable family*
with parameter \( \alpha = 0.4 \), killing rate \( a = 0.1 \),
drift \( b = 0.2 \), and intensity scaling parameter \( \gamma = 0.5 \):

```{r}
rpextmo(
  10, 3,
  a = 0.1, b = 0.2, gamma = 0.5,
  eta = 0.4, family = "AlphaStable",
)
```

## Advance usage

Aside from the integrated families, the `rmo` package also provides tools to 
create custom extendible Marshall–Olkin distributions via so-called *Bernstein
functions*. For example, the following code generates the Bernstein function
associated with the *\( \alpha \)-stable family* with parameter
\( \alpha = 0.4 \) from the simple example above:

```{r}
AlphaStableBernsteinFunction(0.4)
```

The class of Bernstein functions is closed under addition, scalar
multiplication, and composite scalar multiplication. This allows recombinations
of implemented Bernstein functions to create new ones. For example, the following
code creates the Bernstein function associated with the *\( \alpha \)-stable
family* with parameter \( \alpha = 0.4 \), killing rate \( a = 0.1 \),
drift \( b = 0.2 \), and intensity scaling parameter \( \gamma = 0.5 \):

```{r}
SumOfBernsteinFunctions(
  SumOfBernsteinFunctions(
    ConstantBernsteinFunction(0.1),
    LinearBernsteinFunction(0.2)
  ),
  ScaledBernsteinFunction(
    0.5,
    AlphaStableBernsteinFunction(0.4)
  )
)
```

To generate a sample from this custom extendible Marshall–Olkin distribution,
use the `rextmo` function:

```{r}
rextmo(10, 3,
  SumOfBernsteinFunctions(
    SumOfBernsteinFunctions(
      ConstantBernsteinFunction(0.1),
      LinearBernsteinFunction(0.2)
    ),
    ScaledBernsteinFunction(
      0.5,
      AlphaStableBernsteinFunction(0.4)
    )
  )
)
```

## Extending `rmo`

The `rmo` package is designed to be easily extensible. Consider the following 
Bernstein function: 
$$
  \psi(x)
    = \log{\frac{b {(x + a)}}{a {(x + b)}}},
      0 < a < b.
$$

It is a complete Bernstein function with Lévy density \( \nu \):
$$
  \nu{(u)}
    = {\left[ e^{-a u} - e^{-b u} \right]} / {u},
      u > 0 ,
$$
and with the Stieljtes density \( \sigma \):
$$
  \sigma{(u)}
    = 1_{(a, b)}{(u)} / {u},
      u > 0 .
$$

It is not implemented in the package, but it can be added as follows:

```{r}
CustomBernsteinFunction <- setClass( # nolint
  "CustomBernsteinFunction",
  contains = "CompleteBernsteinFunction",
  slots = c(a = "numeric", b = "numeric"),
  validity = function(object) {
    if (object@a <= 0) {
      stop("a must be positive")
    }
    if (object@b <= 0) {
      stop("b must be positive")
    }
    if (object@a >= object@b) {
      stop("a must be less than b")
    }

    invisible(TRUE)
  }
)

setMethod(
  "initialize",
  signature(.Object = "CustomBernsteinFunction"),
  function(.Object, a, b) { # nolint
    if (!missing(a) && !missing(b)) {
      .Object@a <- a # nolint
      .Object@b <- b # nolint
      validObject(.Object)
    }

    invisible(.Object)
  }
)

setMethod(
  "show",
  "CustomBernsteinFunction",
  function(object) {
    cat(sprintf("An object of class %s\n", classLabel(class(object))))
    if (isTRUE(validObject(object, test = TRUE))) {
      cat(sprintf("- a: %s\n", format(object@a)))
      cat(sprintf("- b: %s\n", format(object@b)))
    } else {
      cat("invalid or not initialized object\n")
    }

    invisible(NULL)
  }
)

setMethod(
  "levyDensity",
  "CustomBernsteinFunction",
  function(object) {
    structure(
      function(u) {
        (exp(-object@a * u) - exp(-object@b * u)) / u
      },
      lower = 0, upper = Inf, type = "continuous"
    )
  }
)

setMethod(
  "stieltjesDensity",
  "CustomBernsteinFunction",
  function(object) {
    structure(
      function(u) {
        ifelse(u > object@a & u < object@b, 1 / u, 0)
      },
      lower = object@a, upper = object@b, type = "continuous"
    )
  }
)
```

Now we can create a custom Bernstein function object and generate samples from
it:

```{r}
bf <- CustomBernsteinFunction(a = 0.1, b = 0.2)
rextmo(10, 3, bf)
rexmo(10, 3, exIntensities(bf, 3, method = "levy"))
rexmo(10, 3, exIntensities(bf, 3, method = "stieltjes"))
```

## References
